### 2024-05-14 index.qmd
20240513 - typo
20240514 - cut

![Creative Commons License](Images/CC-BY.png){width=50%}

@@

<!--
[![DOI](Images/zenodo_doiBadge.png)](https://doi.org/10.5281/zenodo.6466589)
-->

@@

```
@book{petersenFantasyFootballAnalytics,
  title = {Fantasy football analytics},
  author = {Petersen, Isaac T.},
  year = {2024},
  publisher = {{University of Iowa Libraries}},
  note = {Version 0.0.1},
  doi = {INSERT},
  isbn = {INSERT},
  url = {https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook}
}
```

@@

I strive to follow [principles of accessibility](https://bookdown.org/yihui/rmarkdown-cookbook/html-accessibility.html) (archived at https://perma.cc/8XJ9-Q6QJ) to make the book content accessible to people with visual impairments and physical disabilities.
If there are additional ways I can make the content more accessible, please let me know.

>>>>

![Creative Commons License](images/CC-BY.png){width=50%}

@@

@@

@@

I strive to follow [principles of accessibility](https://bookdown.org/yihui/rmarkdown-cookbook/html-accessibility.html) (archived at <https://perma.cc/8XJ9-Q6QJ>) to make the book content accessible to people with visual impairments and physical disabilities.
If there are additional ways I can make the content more accessible, please let me know.
